POMDP comparisons across sigma_m, sigma_g

### 2017-10-11 appendix/appendix.Rmd
fix order of meta

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.2), 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
```

@@

```{r eval=TRUE}
log_dir <- "appendix_alphas" # Store the computed solution files here
dir.create(log_dir)

## POMDP solution (slow, >10,000 seconds per scenario, & memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal")

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir) %>% mutate(scenario=as.character(1:length(models)))
alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r pomdp_sims}
# slower!
unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps=reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario") %>% left_join(meta)
```

@@

```{r}
pomdp_sims %>%
  select(time, state, rep, method, sigma_m, sigma_g) %>%
  group_by(time, method, sigma_m, sigma_g) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line() + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.2) +
  facet_grid(sigma_m ~ sigma_g)
```

>>>>

```{r}
meta <- expand.grid(sigma_g = c(0.02, 0.1, 0.2), 
                    sigma_m = c(0, 0.1, 0.2),
                    stringsAsFactors = FALSE) %>%
        mutate(scenario  = as.character(1:length(sigma_m)))
log_dir <- "appendix_alphas" # Store the computed solution files here
meta
```

@@

```{r eval=FALSE}
dir.create(log_dir)

## POMDP solution (slow, >10,000 seconds per scenario, & memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

```{r}
meta <- meta_from_log(data.frame(model="gs"), log_dir) %>% left_join(meta) %>% arrange(scenario)
alphas <- alphas_from_log(meta, log_dir)
```

@@

```{r pomdp_sims}
# slower!
unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario")
```

@@

```{r}
sims %>%
  select(time, state, rep, method, sigma_m, sigma_g) %>%
  group_by(time, method, sigma_m, sigma_g) %>%
  summarise(mean = mean(state), sd = sd(state)) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line() + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.2) +
  facet_grid(sigma_m ~ sigma_g)
```
